---
title: "Lab N - Lab Title"
author: "First Last"  
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
    code_folding: show
    theme: simplex
    highlight: tango
editor_options: 
  chunk_output_type: console
---

This report (add a brief description and the purpose of the report)
Demonstration of the __COMBINED__ template

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F, results = 'hide'}
cat("Working directory: ", getwd()) # turn on to test the location
# if the line above generates the project root, re-map by selecting 
# Session --> Set Working Directory --> To Source File location
```


```{r set_options, echo=F}
# cat("Working directory: ", getwd()) # turn on to test the location
report_render_start_time <- Sys.time()
# set options shared by all chunks
knitr::opts_chunk$set(
  results      = 'show',
  message      = FALSE,
  warning      = FALSE,
  comment      = NA,
  tidy         = FALSE,
  # dpi        = 400, # dots per inch,
  # out.width  = "650px", # pixels, this affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 6, # inches
  fig.height   = 4, # inches
  fig.path     = 'figure-png-com/' # where figures are stored
)
echo_chunks    <- FALSE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) # number of characters to display in the output (dflt = 80)
ggplot2::theme_set(ggplot2::theme_bw()) # common theme for all graphs
```

# Environment
<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, message=message_chunks}
library(magrittr)  # pipes
library(dplyr)     # data wrangling
library(ggplot2)   # graphs
library(janitor)   # tidy data
library(tidyr)     # data wrangling
library(forcats)   # factors
library(stringr)   # strings
library(lubridate) # dates
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources}
source("../../scripts/common-functions.R")
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals}
# custom function for HTML tables
neat <- function(x, output_format = "html"){ 
  # knitr.table.format = output_format
  if(output_format == "pandoc"){
    x_t <- knitr::kable(x, format = "pandoc")
  }else{
    x_t <- x %>%
      # x %>%
      # neat() %>%
      knitr::kable(format=output_format) %>%
      kableExtra::kable_styling(
        bootstrap_options = c("striped", "hover", "condensed","responsive"),
        # bootstrap_options = c( "condensed"),
        full_width = F,
        position = "left"
      )
  } 
  return(x_t)
}
# Note: when printing to Word or PDF use `neat(output_format =  "pandoc")`
```



# Data
```{r load-data, results='show', message=FALSE}
path_file <- "../../data-public/raw/Tableau_10_Training_Files/Tableau 10 Training Practice Data.xlsx"
sheet_names <- readxl::excel_sheets(path_file)
dto <- list()
for(sheet_i in sheet_names){
   # i <- sheet_names[1]
  dto[[sheet_i]] <- readxl::read_xlsx(path_file, sheet = sheet_i)
}
ds_raw <- dto$`01 - Preoperative Risk Factors`
```

```{r tweak-data,echo = echo_chunks, results='show', message=message_chunks}
ds0 <- ds_raw %>% 
  janitor::clean_names() # because lowercase is easier to type and remember
ds0 %>% glimpse()
```

# Analysis

```{r table-1, echo = echo_chunks, results='show', message=message_chunks}
ds0 %>% neat()
```

```{r graph-1, echo = echo_chunks, results='show', message=message_chunks}
ds0 %>% 
  ggplot(aes(y=hospital_percent, x = preoperative_risk_factors))+
  geom_col(fill="salmon", alpha = .5, color = "black")+
  coord_flip()+
  labs(title = "Graph 1")
```

```{r graph-2, echo = echo_chunks, results='show', message=message_chunks}
g2 <- ds0 %>% 
  ggplot(aes(y=risk_factors_count, x = preoperative_risk_factors))+
  geom_col(fill = "skyblue", alpha = .5, color = "black")+
  coord_flip()+
  labs(title = "Graph 2")
g2
```

Session Information {#session-info}
===========================================================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
}
```
</details>

```{r session-duration, echo=FALSE}
report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.
